### 2015-11-10 LaTeX/RhodiumAppendix.tex
fixed typos and stuff
final cleanups
incorp updated tables to rev letter and new appendix item
FE appendix blurb and footnote.

\section{Appendix}
\label{appendix}

@@

\input{baseline.tex}

@@

\FloatBarrier
\nepage

@@

@@

\input{acledModels.tex}
\FloatBarrier

>>>>

\newpage
\section{Appendix}
\label{appendix}

@@

\input{baseline.tex}
\FloatBarrier
\newpage

@@

\FloatBarrier
\newpage

@@

\newpage
\subsection{Full Panel Fixed Effects Analysis}

While we contend that random effects are preferred to fixed effects for the reasons outlined in the body of the paper, we have nonetheless repeated our analysis using fixed effects. The results are presented in Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}. These analyses are performed on the full panel of data and therefore are missing conflict-specific covariates that are unavailable for countries not experiencing civil war.

City models
\input{cityFullPiecewiseFE.tex}
\FloatBarrier

Capital models
\input{capFullPiecewiseFE.tex}
\FloatBarrier

@@

\input{acledModels.tex}
\FloatBarrier
\newpage

### 2015-11-10 LaTeX/RhodiumEmp.tex
FE appendix blurb and footnote.

%A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time; rather our purpose is to explain variation between units. However,
To estimate variation in growth rates, we use a random effects model clustered on countries. To ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}. For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, which provides at least some initial evidence that we are justified in our choice. However, as \citet{clark:linzer:2015} note, the Hausman test should not be the sole determinant for choosing between fixed or random effects. We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{Specifically, they suggest taking into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects. In our case, we have over 70 countries but for over half of those we only have five conflict instances or less. Given such a data structure, Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework. For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).}

>>>>

%A random effects specification is preferred to using fixed effects here as we are not interested in estimating the change in GDP within units over time; rather our purpose is to explain variation between units. However,
To estimate variation in growth rates, we use a random effects model clustered on countries. To ensure that it is statistically justifiable to make this choice we run a Hausman specification test \citep{greene:2008}.\footnote{Fixed effects models can be found in the Appendix, Tables~\ref{tab:cityFullPiecewiseFE} and \ref{tab:capFullPiecewiseFE}.} For both the minimum conflict distance to any and to capital city specifications we fail to reject the null hypothesis at both the 90 and 95\% confidence intervals, which provides at least some initial evidence that we are justified in our choice. However, as \citet{clark:linzer:2015} note, the Hausman test should not be the sole determinant for choosing between fixed or random effects. We utilize their more nuanced typology for further arbitrating between fixed and random effects, and again we find that random effects are preferred in this case.\footnote{Specifically, they suggest taking into consideration the size of the dataset (both number of units, in this case countries, and number of observations per unit, conflict instances) and the level of correlation between the regressor and unit effects. In our case, we have over 70 countries but for over half of those we only have five conflict instances or less. Given such a data structure, Clark \& Linzer (2015) recommend to examine the level of correlation between the regressor and unit effects to determine the appropriate modeling framework. For both our distance models, the level of correlation between the regressor and unit effects is less than 0.20, which accords with a random effects recommendation under the framework described by Clark \& Linzer (2015).}
